SPARQL on the Open, Decentralised Web

### 2016-07-22 dissertation/introdefhistory.tex
divide sentence

I was convinced that the things that made the Web great to work with
had to be present in the Semantic Web as well: Everybody is empowered
to publish, find and quickly make use of Free Software, learn by
``View Source'' (an idea which becomes even more powerful with
semantics, as if you can understand what you are viewing simply by
looking at the message, you can begin processing it), anyone can mint
identifiers and anybody can reuse those identifiers in their own
contexts, and eventually graduate to reading technical materials as
needed. Many of these things are virtues of the Semantic Web as it is
an extension of the Web, others have not been sufficiently cultivated
or even appreciated. Moreover, my experience corresponds with the
virtues that Tim Berners-Lee has attributed the Web's success\footnote{See
  \url{http://dig.csail.mit.edu/2007/03/01-ushouse-future-of-the-web}}.

>>>>

I was convinced that the things that made the Web great to work with
had to be present in the Semantic Web as well: Everybody is empowered
to publish, find and quickly make use of Free Software, learn by
``View Source'' (an idea which becomes even more powerful with
semantics, as if you can understand what you are viewing simply by
looking at the message, you can begin processing it). Also, anyone can mint
identifiers and anybody can reuse those identifiers in their own
contexts, and eventually graduate to reading technical materials as
needed. Many of these things are virtues of the Semantic Web as it is
an extension of the Web, others have not been sufficiently cultivated
or even appreciated. Moreover, my experience corresponds with the
virtues that Tim Berners-Lee has attributed the Web's success\footnote{See
  \url{http://dig.csail.mit.edu/2007/03/01-ushouse-future-of-the-web}}.
